Replication Survey

### 2023-08-01 docs/manuscript/manuscript.tex
Completed Fig 2 write up

\begin{itemize}
    \item Minimal variation in responses across method groups or sub-fields. 
\end{itemize}

\vspace{5mm}

@@

Phenomena
\begin{itemize}
    \item Spatial dependence lean to decrease chance of replication (41.0\%), but notable percentage of respondents (21.6\%) indicated not having a clear idea of whether this would matter.
    \item Belief that strong relationship between a phenomenon and local conditions reduced chances of replication (59.7\%)
    \item Fairly even spread across increase, decrease, no effect on exhibits variation across space.
    \item When a phenomenon cannot be directly measured decreases chance of replication (61.5\%).
    \item Really even distribution on nearly a phenomenon characteristics. Also a decently high percentage of i don't know resposnes for each characteristic. In most cases in the 10-20 percent range. 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Factors that Affect the Decision to Attempt Replications}
Several factors appear to affect whether researchers decide to attempt to replicate recent geographic research.
Figure \ref{fig:Q15-DecisionFactors} presents how frequently respondents believe differences in academic incentives (AI), the availability of research artifacts (AA), and study characteristics (SC) affect researchers' decisions to attempt to replicate existing geographic research.
Response characteristics for each factor are recorded at the right of the figure.

@@

Geographic researchers identified current academic incentives as the factor most frequently impacting the decision to attempt a replication study. 
A majority of respondents identified the pressure to publish original research (66\%) and the lack of funding for replication studies (59\%) as frequently or always impacting the decision to attempt a replication.
Respondents also believed that the perception of replications as low value work (55\%) that was often difficult to publish (51\%) also impacted decision making.  
Contrary to some narratives in the replication literature, the desire to identify fabricated data or results was not seen as a determining factor in the decision to attempt a replication. 
However, this finding should be interpreted with caution as a third of respondents indicated that they did not know whether potential fabrication influenced researcher decision making.

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.8]{results/figures/Fig-Q8-10-Chances.png}
    \caption{Factors affecting the chances of replicating a study. Respondents identified (a) how likely study characteristics were to alter the chances of successfully replicating a study and (b) how likely the characteristics of the phenomenon under investigation were to alter the chances of successfully replicating a study in a new location. Acronyms indicate: artifact accessibility (AA), researcher characteristics (RC), study approach (SA), and phenomenon characteristics (PC); and the percentage of `don't know' (DK) and missing (M) responses. Unlikely to affect replication chances is omitted, but can be calculated from available data.}
    \label{fig:Q8-10-Chances}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.80]{results/figures/Fig-Q15-Decisions.png}
    \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies. Factors grouped by: Academic Incentives (AA), Artifact Accessibility (AA), Study Characteristics (SC).}
    \label{fig:Q15-DecisionFactors}
\end{figure}

>>>>

@@

There was less agreement among respondents about whether different characteristics of a phenomenon would impact the chances of replicating the claims made by a prior study of that phenomenon (Figure \ref{fig:Q8-10-Chances}b). 
For all six of the characteristics we examined, at least 12 percent of respondents replied that those factors would have no effect on the chances of replicating a prior study.
Numerous respondents also replied that they the simply did not know whether a characteristic would impact the chances of replicating a study. 
For example, 20 percent of respondents said they did not know whether a phenomenon being spatially dependent with itself would affect the chances of replicating a prior study, and an additional 15 percent of respondents said spatial dependence would have no effect on replication. 
Even with this uncertainty, 41 percent of respondents said the presence of spatial dependence was likely to decrease the chances of replicating a prior study.

A majority of respondents did identify the inability to directly measure a phenomenon (61.5\%) and a strong relationship between a phenomenon and local conditions (59.7\%) as reducing the chances of replicating a prior study.
Respondents were roughly evenly divided on whether other factors would increase or decrease the chances of replicating a study.
Respondents also favored 'somewhat likely' responses over stronger 'very likely' responses across all characteristics, which further suggests that absence of a clear consensus understanding of how these factors relate to and impact replication.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Factors that Affect the Decision to Attempt Replications}
Several factors appear to affect whether researchers decide to attempt to replicate recent geographic research (Figure \ref{fig:Q15-DecisionFactors}).
Geographic researchers identified current academic incentives as the factor most frequently impacting the decision to attempt a replication study. 
A majority of respondents identified the pressure to publish original research (66\%) and the lack of funding for replication studies (59\%) as frequently or always impacting the decision to attempt a replication.
Respondents also believed that the perception of replications as low value work (55\%) that was often difficult to publish (51\%) also impacted decision making.  
Contrary to some narratives in the replication literature, the desire to identify fabricated data or results was not seen as a determining factor in the decision to attempt a replication. 
However, this finding should be interpreted with caution as a third of respondents indicated that they did not know whether potential fabrication influenced researcher decision making.

@@

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.8]{results/figures/Fig-Q8-10-Chances.png}
    \caption{Factors affecting the chances of replicating a study. Respondents identified (a) how likely study characteristics were to alter the chances of successfully replicating a study and (b) how likely the characteristics of the phenomenon under investigation were to alter the chances of successfully replicating a study in a new location. Acronyms indicate: artifact accessibility (AA), researcher characteristics (RC), study approach (SA), and phenomenon characteristics (PC); and the percentage of no effect (NE), `don't know' (DK), and missing (M) responses.}
    \label{fig:Q8-10-Chances}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.80]{results/figures/Fig-Q15-Decisions.png}
    \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies. Factors grouped by: Academic Incentives (AA), Artifact Accessibility (AA), Study Characteristics (SC); and the percentage `don't know' (DK) and missing (M) responses.}
    \label{fig:Q15-DecisionFactors}
\end{figure}
